The problem and promise of scale in animal social multilayer networks

### 2020-02-07 paper/manuscript.Rmd
update title
rm grain, extent

---
title: The problem and promise of scale in multilayer networks
author: Alec L. Robitaille^1^, Quinn M.R. Webber^2^, Julie W. Turner^1^, Eric Vander Wal^1,2^
date: ^1^Department of Biology, Memorial University of Newfoundland, Canada; ^2^Cognitive and Behavioural Ecology Interdisciplinary Program, Memorial University of Newfoundland
output:
  # github_document
  # bookdown::pdf_document2:
  #    number_sections: false
  bookdown::word_document2:
    reference_docx: template.docx
bibliography: ../references/knitcite.bib
---

@@

# Abstract
Scale remains a seminal concept in ecology. Spatial scale, for instance, has
become a central consideration in the way we understand landscape ecology and
animal space use. Meanwhile, social processes can also scale from fine-scale
interactions to co-occurrence to overlapping home ranges. Multilayer networks
promise the integration of monolayer animal social networks with the complexity
and importance of animal space use and movement in heterogeneous landscapes.
Despite the complex interplay between social networks and how animals use space,
there remains an important biological and methodological gap in our
understanding of an animal’s perception of scale, e.g., grain and extent. But
scale can affect multilayer network dynamics and how we build and interpret
them. Here we discuss the role of scale in the context of multilayer networks
and provide a case study of caribou (*Rangifer tarandus*) to illustrate the role
of social, spatial, and temporal scale on multilayer processes. We also present
perspectives on future development and application of scale in multilayer
networks with respect to habitat selection and space use, individual fitness and
phenotypes, and movement ecology and collective movement. Effective integration
of social and spatial processes, including biologically meaningful scales,
within the context of animal social networks is an emerging area of research;
our contribution uniquely incorporates perspectives on how the social
environment and spatial processes are linked across scales in a multilayer
framework. Based on social network and behavioural ecology theory as well as our
case study, we demonstrate potential for interconnectedness among individual
animals, their social environment, and the landscapes they occupy.

>>>>

---
title: The problem and promise of scale in animal social multilayer networks
author: Alec L. Robitaille^1^, Quinn M.R. Webber^2^, Julie W. Turner^1^, Eric Vander Wal^1,2^
date: ^1^Department of Biology, Memorial University of Newfoundland, Canada; ^2^Cognitive and Behavioural Ecology Interdisciplinary Program, Memorial University of Newfoundland
output:
  # github_document
  # bookdown::pdf_document2:
  #    number_sections: false
  bookdown::word_document2:
    reference_docx: template.docx
bibliography: ../references/knitcite.bib
---

@@

# Abstract
Scale remains a seminal concept in ecology. Spatial scale, for instance, has
become a central consideration in the way we understand landscape ecology and
animal space use. Meanwhile, social processes can also scale from fine-scale
interactions to co-occurrence to overlapping home ranges. Multilayer networks
promise the integration of monolayer animal social networks with the complexity
and importance of animal space use and movement in heterogeneous landscapes.
Despite the complex interplay between social networks and how animals use space,
there remains an important biological and methodological gap in our
understanding of an animal’s perception of scale. But
scale can affect multilayer network dynamics and how we build and interpret
them. Here we discuss the role of scale in the context of multilayer networks
and provide a case study of caribou (*Rangifer tarandus*) to illustrate the role
of social, spatial, and temporal scale on multilayer processes. We also present
perspectives on future development and application of scale in multilayer
networks with respect to habitat selection and space use, individual fitness and
phenotypes, and movement ecology and collective movement. Effective integration
of social and spatial processes, including biologically meaningful scales,
within the context of animal social networks is an emerging area of research;
our contribution uniquely incorporates perspectives on how the social
environment and spatial processes are linked across scales in a multilayer
framework. Based on social network and behavioural ecology theory as well as our
case study, we demonstrate potential for interconnectedness among individual
animals, their social environment, and the landscapes they occupy.
